Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-22 sections/eval.tex
Update on Overleaf.

\begin{table}[htbp]
    \centering
    \caption{SpMV Sample Matrices}
    \label{spmv_sample_matrices}
    \begin{tabular}{|m{3cm}|c|c|c|}
        \hline
        \textbf{Spy} & \textbf{Group / Name} & \textbf{Dimensions} & \textbf{Best Finch Format}\\
        \hline
        \includegraphics[width=3cm]{spmv_matrices/saylr4.png} & HB/saylr4 & 3,564 x 3,564 (22,316) & Symmetric SparseList \\
        \hline 
        \includegraphics[width=3cm]{spmv_matrices/heart3.png} & Norris/heart3 & 2,339 x 2,339 (680,341) & SparseVBL \\
        \hline 
        \includegraphics[width=3cm]{spmv_matrices/as-735.png} & SNAP/as-735 & 7,716 x 7,716 (26,467) & Symmetric SparseList-Pattern \\
        \hline
    \end{tabular}
\end{table}

@@

\begin{minted}{julia}
            @finch begin
                for J = _
                    for I = _
                        for j = 1:10
                            for i = 1:10
                                let _i = (I - 1) * 10 + i
                                    y[_i] += block_A[i, j, I, J] * block_x[j, J]
                                end
                            end
                        end
                    end
                end
            end
\end{minted}

>>>>

\begin{table}[htbp]
    \centering
    \caption{SpMV Sample Matrices}
    \label{spmv_sample_matrices}
    \begin{tabular}{|m{3cm}|c|c|c|}
        \hline
        \textbf{Spy} & \textbf{Group / Name} & \textbf{Dimensions} & \textbf{Best Finch Format}\\
        \hline
        \includegraphics[width=3cm]{spmv_matrices/saylr4.png} & HB/saylr4 & 3,564 x 3,564 (22,316) & Symmetric SparseList \\
        \hline 
        \includegraphics[width=3cm]{spmv_matrices/heart3.png} & Norris/heart3 & 2,339 x 2,339 (680,341) & SparseVBL \\
        \hline 
        \includegraphics[width=3cm]{spmv_matrices/toeplitz_large_band.png} & toeplitz\_large\_band  & 10,000 x 10,000 (1,999,900) & SparseBand \\
        \hline
        \includegraphics[width=3cm]{spmv_matrices/as-735.png} & SNAP/as-735 & 7,716 x 7,716 (26,467) & Symmetric SparseList-Pattern \\
        \hline
    \end{tabular}
\end{table}

@@
